\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
break 80 line char
one X forgotten

Then we apply on the entire signal a non-linear filter based on the
current activity of the systems in order to favor the association measure inversely
proportional to the number of neurons firing together:
$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $.
When too much neurons are firing together, i.e. in case of a network burst, it is almost
impossible to retrieve direct relationships: all neurons seem to be directly
connected to each other. By favoring the association measure when the activity is low,
we expect to retrieve a pair of neurons that are really directly connected together.
In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function
of the activity of all neurons but the number and the locations of peaks is not modified.

>>>>

Then we apply on the entire signal a non-linear filter based on the
current activity of the systems in order to favor the association measure inversely
proportional to the number of neurons firing together:
$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x_{t,d}^j}} $.
When too much neurons are firing together, i.e. in case of a network burst, it is almost
impossible to retrieve direct relationships: all neurons seem to be directly
connected to each other. By favoring the association measure when the activity is low,
we expect to retrieve a pair of neurons that are really directly connected together.
In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function
of the activity of all neurons but the number and the locations of peaks is not modified.
